### 2023-06-07 Article.Rmd
The present study setup
literature review - refacut

## Literature review
In the past few years, social media has risen to become a significant means of communication between public institutions and citizens. This has paved the way for increased citizen engagement in the decision-making process, which is considered essential for fostering trust and enhancing accountability. This literature review delves into the significance of citizen involvement in the communication process of public institutions via social media. It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union.

@Bene2022 conducted a study exploring the impacts of self-centered social media communication styles on user engagement across 12 European nations. Their findings revealed that social media communication emphasizing user participation and fostering feedback effectively boosts user engagement. Social media users who feel they have a say in the decision-making process are more inclined to engage and participate in conversations. @DeWilde2022 examined citizen engagement with European politics on social media platforms and discovered that social media holds the potential to increase citizen involvement and participation in the political sphere. They found that social media offers citizens a platform to express their opinions, partake in discussions, and influence policy-making decisions. In a similar vein, @Bankston2021 investigated the role of social media in migration and smuggling across the European Union's virtual borders. This study concluded that social media platforms offer citizens opportunities to engage in dialogues and share their perspectives on immigration policies.

@Cinelli2022, on the other hand, delved into promoting engagement with quality communication in social media. Their findings indicated that employing persuasive language, evoking emotions, and utilizing framing can enhance user engagement. The study recommends that public institutions implement quality communication techniques to boost citizen engagement and participation in policy-making. @Muller2022 analyzed the social media attention garnered by European Union agencies and found a positive correlation between increased attention and higher levels of citizen engagement. This study implies that public institutions can augment citizen engagement by effectively utilizing social media to showcase their activities and interact with citizens.

Additionally, @Rus2021 carried out a case study investigating the representation of the European Commission in Romania via social media communication. The study established that social media communication by public institutions can bolster transparency and accountability, consequently leading to heightened citizen engagement. @Hancu2020 examined the communication strategies employed by audit institutions in the European Union during the Covid-19 crisis. Their findings suggested that social media can serve as a potent tool for promoting public services and encouraging environmental engagement. The study advocates for public institutions to harness social media to showcase their activities and connect with citizens during times of crisis. @Kanol2021 scrutinized the social media engagement tactics of British interest groups on Facebook. They found that group type influences social media engagement strategies, with non-profit groups being more inclined to utilize user-generated content and participatory approaches. The study implies that public institutions can adopt lessons from non-profit groups and employ participatory strategies to elevate citizen engagement.

Finally, @Wei2021 executed a case study analyzing public opinions on climate change policy in the European Union using Twitter data. The study concluded that social media offers a platform for citizens to discuss climate change policies, suggesting that public institutions should leverage social media to engage with citizens on critical issues like climate change.

# Case study
## Research objectives
The overall objective of this research is to analyze and compare the online engagement of the public on various official social media platforms (Facebook, Instagram, Twitter, and YouTube) of the European Commission.

## Research tool
The research instrument used in this study involved the extraction and analysis of data from the official Facebook, Twitter, Instagram, and Youtube pages of the European Commission. To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.

The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023.

To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers. This metric is often used to measure the level of audience interaction with a brand or organization on social media.

@@

In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023. We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.

>>>>

## Literature review
In studying the impact of citizen engagement on the European Commission's social media platforms, it is crucial to discern the key concepts that underpin this research. These concepts are engagement, social media platforms, and sentiment analysis, which form the backbone of many academic discourses that revolve around these themes.

Engagement, defined as the active interaction of users with digital content, is a fundamental element of any effective social media strategy. It encapsulates various forms of participation, from comments and shares to likes and views [@Mirbagheri2019]. @Smith2015 argue that engagement helps in establishing profound relationships with users, and it can vary according to the type of platform [@Voorveld2018]. The concept has found applicability in numerous contexts, including public health [@heldmanSocialMediaEngagement2013], student learning (Dragseth, 2020), and corporate social responsibility (@doncel-martinCorporateSocialResponsibility2023].

The significance of engagement reaches a higher dimension in the political and public sphere. With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies (@Muller2022]. There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022]. This interaction has been correlated with a spectrum of outcomes, such as influencing voting behavior [@marquartThisTimeNot2020] and attitudes towards vaccination [@mascheriniSocialMediaUse2022].

Simultaneously, social media platforms are becoming recognized as powerful tools for promoting and managing engagement. This dual role is exemplified in the case of the European Commission's activities in Romania [@Rus2021]. Recognizing the potential of these platforms to facilitate citizen engagement, EU institutions have taken steps to optimize their use, implementing various strategies [@Bene2022; @Kanol2021; @ozdemirBirdEyeView2022].

In assessing the impact of citizen engagement on the EU's social media platforms, researchers employ an assortment of methods, one of which is sentiment analysis. This approach, which involves the systematic identification and categorization of the emotional tone behind words, aims to gauge public sentiment, attitudes, and emotions towards specific topics [@Wei2021]. It has been applied in diverse contexts, such as analyzing the emotional distribution in EU smart city communication [@kowalikSocialMediaDistribution2021] and exploring public opinions on climate change policy [@Wei2021].

The European Union’s social media landscape is remarkably complex, as shown by numerous studies. These platforms can simultaneously facilitate positive engagement, such as public service promotion [@Hancu2020], and breed negative phenomena like hate speech [@doncel-martinCorporateSocialResponsibility2023] and digital vigilantism [@allenDigitalVigilantismSocial2020]. Furthermore, the influence of these platforms is shaped by broader societal and political developments, such as migration and smuggling across virtual borders [@Bankston2021].

To sum up, understanding the impact of citizen engagement on the European Commission's social media platforms is a multifaceted issue. These platforms offer opportunities for meaningful citizen engagement and public communication, but their influence is dictated by a complex interplay of individual behavior, institutional strategy, societal trends, and technological developments. This complexity calls for a nuanced understanding of each constituent factor and their collective role in shaping the landscape of citizen engagement within the context of the European Commission's social media platforms. It is a call to researchers, policymakers, and practitioners to continuously explore this evolving realm to maximize the benefits of citizen engagement while mitigating its potential pitfalls.

# Case study
## Research objectives
The primary objective of this research is to conduct a quantitative and qualitative analysis of public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube). This will involve comparing and contrasting the patterns, trends, and characteristics of online user interactions and responses across these platforms.

## Research method
The research methodology employed in this study involved the extraction and subsequent analysis of data derived from the official Facebook, Twitter, Instagram, and YouTube channels of the European Commission. To amass this data, we utilized the Fanpagekarma platform, a prevalent tool for conducting analytics and monitoring on social media platforms.

The data procured from this platform encompassed a range of elements, including post ID, message content, post type, post date, number of likes, comments, shares, and the rounded figure of followers for each post made by the European Commission in the period from the 3rd of February 2019 to the 23rd of April 2023.

In order to quantify the engagement rate, we calculated the total number of reactions (comprising likes, comments, and shares), and divided it by the total follower count. This engagement rate metric is commonly employed to gauge the extent of audience interaction with a brand or organization on social media platforms. To achieve the research objective, we employed a sentiment analysis method.

## The present study
H1: Communications with emotional resonance are associated with higher public engagement levels.
H2: The effect of emotional resonance on public engagement is moderated by the social media platform utilized.

@@

In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from `3 February 2019 to 23 April 2023. We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.
